---
title: "R Notebook"
output: html_notebook
---

```{r echo = F}
library(ggplot2)
library(dplyr)
library(caret)

load("dados//films.Rdata")
```

# Data structure

We have 6 data frames in total. The string "\\N" is used to encode missing values. We have replaced them by *NA* in order to take advantage of the default methods to isolate these values. The 6 data frames are:

## **t_basics**

* **t_basics** contains basic information about the items: movies, films. **tconst** is the primary key that links this dataframe to the others.

* It is a premise of this work that data concerning series will not be considered. This information is defined in the variable **titleType**. We can exclude right away the following types: 

  * "tvEpisode","tvMiniSeries","tvSeries","videoGame"
  
* There is a considerable ammount of missing values in the variables **startYear**, **endYear**, **runtimeMinutes** and **genres**. 
  
* **startYear** appears to function as "Release Year" in the titles that do not have an episodic format.

* Columns 
  
* **genre** is a concatenated string. Considering we are certain to be interested in this information, a solution to extract this data to an usable format must be found.
  
```{r}
apply(t_basics,2,function(x){sum(is.na(x))})
```
  
  
## **crew**  
  
* **crew** has 2 unique fields: **directors** and **writers**. 

  * There are 262500 missing values in **directors** and 647145 in **writers**. This a considerable part of the 1.8 M total observations.

```{r}
apply(crew,2,function(x){sum(is.na(x))})
```

* **ratings** is, by its nature, one of the most promising data frames. Its two variables, **averageRating** and **numVotes** are direct, quantifiable measures of the success of a title. 

  * This data frame has no missing values. **averageRating** has all its entries in the $[1,0]$ range, as expected, and the **numVotes** are in the $[5,2966829]$ range. The title with the maximum number of votes is "The Shawshank Redemption", which is plausible. 
  
  * This data frame appears to function as the core of the dataset, in the sense that as long as a title has a valid entry in this table, gaps in the associated tables are tolerated. 

```{r}
apply(ratings,2,function(x){sum(is.na(x))})
summary(ratings)
t_basics[t_basics$tconst == ratings[which.max(ratings$numVotes),]$tconst,]
```

* **akas** contains information about the regional adaptations of the films. 

  * The variable **title** is an encoding disaster and is best ignored. 
  
  * No performance metrics aree available for each separate version, so it stands to be determined whether the corresponding entry in **ratings** is an aggregated score, average or it pertains only to the main release

```{r}
apply(akas,2,function(x){sum(is.na(x))})
```

* **principals** contains information about the cast and team behind a title. 

* **n_basics** is an auxiliary table with information on people of interest that are referenced in the **principals** data frame. 

  * The variable **primaryProfession** and **knownforTitles** are concatenated strings which may prove problematic if we decide focus our analysis in the crew facet of the matter.


## Data pre processing

### Splitting concatenated strings

Should we consider one-hot encoding? There are 30 genres in total.

```{r}
#how many genres are at maximum?
stringr::str_count(t_basics$genres,",") %>% max(na.rm = T)
#maximum 2 commas, so each title has 3 genres max
t_basics <- cbind(t_basics,
                  read.csv(textConnection(t_basics[["genres"]]),row.names = NULL,header = F)
                  )

generos <- unique(reshape2::melt(t_basics,
                                 measure.vars = c("V1","V2","V3"))$value)

temp<- merge(t_basics,
             ratings,
             by = "tconst",
             all.x = T, all.y = F)
temp <-
  merge(temp,
        crew,
        by = "tconst",
        all.x = T, all.t = F)

## Encoder

encoder<-caret::dummyVars("~.",data=temp[,c("V1","V2","V3")])
funcionou<-predict(encoder,newdata=temp[,c("V1","V2","V3")])
funcionou <- data.frame(funcionou)

  for(i in generos[-c(17,30)]){
    funcionou[,paste(i)] <-
    funcionou %>% select(names(funcionou)[grepl(i,names(funcionou))]) %>%
    apply(1,sum,na.rm =T)}

temp <- cbind(temp,funcionou[,84:111])

temp_long <- temp %>% reshape2::melt(measure.vars = 
```


Uma das possibilidades poderia ser  tentar verificar se algum gênero teve  alguma mudança(em relação as votações e ratings) em 2020 em relação aos anos anteriores. 

Essa mudança poderia ser influenciada pela pandemia, quarentena, etc. Ou seja...se as pessoas estão a ver algum gênero de filme com mais frequência em 2020, em comparação com anos anteriores.


[12:40 PM, 10/31/2020] +351 918 508 734: Outra possibilidade seria verificar como a pandemia diminuiu a produção de filmes(títulos lançados).



```{r}
ls()
head(t_basics)
```




uso do IMDB

```{r}



temp %>%
  filter(startYear %in% c(1980:2020)) %>%
  ggplot() + 
  geom_bar(stat = "identity", aes(
    x = cut_width(startYear, 10, center = 2005), 
    y = numVotes), col = rgb(147/255,191/255,235/255)) +
  theme_light() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  scale_x_discrete(breaks = c((cut_width(temp$startYear, 10, center = 2005) %>% levels)[12],
                              (cut_width(temp$startYear, 10, center = 2005) %>% levels)[13],
                              (cut_width(temp$startYear, 10, center = 2005) %>% levels)[14],
                              (cut_width(temp$startYear, 10, center = 2005) %>% levels)[15]),
                     labels = c("1980-1990","1990-2000","2000-2010","2010-2020"))


# temp %>% filter(startYear > 1950) %>%
#   group_by(startYear) %>%
#   summarise(lançamentos = length(unique(tconst))) %>%
# ggplot() + 
#   geom_bar(stat = "identity", aes(x = startYear, y = numVotes), binwidth = 10) + 
#   theme_light() + 
#   theme(axis.text.x = element_text(angle = 90))
(cut_width(temp$startYear, 10, center = 2005) %>% levels)[12]
```

# Plots

```{r}
temp %>%
  filter(startYear %in% c(1980:2020) &
           titleType == "movie") %>%
  ggplot() + 
  geom_bar(stat = "identity", aes(
    x = startYear, 
    y = numVotes), fill = rgb(147/255,191/255,235/255)) +
  theme_light() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  facet_grid(titleType~.)

```



```{r}
#produçao por ano
temp %>% filter(startYear %in% c(1980:2020) &
                  titleType == "movie") %>%
  group_by(startYear) %>%
  summarise(lançamentos = length(unique(tconst))) %>%
ggplot() +
  geom_bar(stat = "identity", aes(x = startYear, y = lançamentos),
           fill = rgb(147/255,191/255,235/255)) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "releases")

temp %>%
  filter(startYear %in% c(1980:2020) &
           titleType == "movie") %>%
  ggplot() + 
  geom_point(aes(x = numVotes,
                 y = averageRating,
                 col = (startYear == 2020))) + 
  theme_light() + 
  scale_color_manual(values = c(rgb(147/255,191/255,235/255),"red"))

```



```{r}
#comparar por generos
temp %>% filter(startYear %in% c(1980:2020) &
                  titleType == "movie") %>%
  ggplot() + 
  geom_boxplot(data = (. %>% filter(Action == 1)), aes(y = averageRating)) +
  geom_boxplot(data = (. %>% filter(Romance == 1)), aes(y = averageRating, x = 1)) +
  geom_boxplot(data = (. %>% filter(Documentary == 1)), aes(y = averageRating, x = 2)) +
  geom_boxplot(data = (. %>% filter(Drama == 1)), aes(y = averageRating, x = 3)) +
  geom_boxplot(data = (. %>% filter(Comedy == 1)), aes(y = averageRating, x = 4)) +
  geom_boxplot(data = (. %>% filter(Music == 1)), aes(y = averageRating, x = 5)) +
  theme_light() + 
  labs(x = "") + 
  facet_grid(as.character(startYear == 2020)~.,labeller = labeller(c("FALSE" = "A", "TRUE" = "B"))) + 
  scale_x_continuous(breaks = seq(0,5,1),labels = c("Action","Romance","Documentary","Drama","Comedy","Music"))

```



```{r}
temp %>% filter(startYear %in% c(1980:2020) &
                  titleType == "movie") %>%
  group_by(startYear, Action) %>%
  summarise(releases = length(unique(tconst))) %>%
  ggplot() + 
  geom_boxplot(data = (. %>% filter(Action == 1)), aes(y = releases)) +
  # geom_boxplot(data = (. %>% filter(Romance == 1)), aes(y = releases, x = 1)) +
  # geom_boxplot(data = (. %>% filter(Documentary == 1)), aes(y = releases, x = 2)) +
  # geom_boxplot(data = (. %>% filter(Drama == 1)), aes(y = releases, x = 3)) +
  # geom_boxplot(data = (. %>% filter(Comedy == 1)), aes(y = releases, x = 4)) +
  # geom_boxplot(data = (. %>% filter(Music == 1)), aes(y = releases, x = 5)) +
  theme_light() + 
  labs(x = "") + 
  facet_grid(as.character(startYear == 2020)~.) + 
  scale_x_continuous(breaks = seq(0,5,1),labels = c("Action","Romance","Documentary","Drama","Comedy","Music"))

```



```{r}
# produçao de generos por ano

temp %>%
  filter(startYear %in% c(1980:2020) &
         titleType == "movie") %>%
  select(startYear,Action,Romance,Documentary,Drama,Comedy,Music) %>%
  reshape2::melt(measure.vars = c("Action","Romance",
                                  "Documentary","Drama","Comedy","Music")) %>%
  group_by(startYear,variable) %>%
  summarise(value = sum(value)) %>%
  ggplot() + 
  geom_boxplot(aes(y = value, col = variable)) + 
  geom_boxplot(data = (. %>% filter(startYear == 2020)),aes(y = value, fill = variable), col = "red") + 
  theme_light() + 
  # facet_grid(as.character(startYear == 2020)~.) +
  labs(col = "", x = "", y = "releases") + 
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(-0.3,0.3,0.12),labels = c("Action","Romance","Documentary","Drama","Comedy","Music"))

```







